---
title: "15_Plots_comparing_GBEV_values"
author: "Paulo-HR"
date: "2023-10-31"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

###################
#
## Introduction
#
###################
```{r}
library(genomicMateSelectR)
library(reshape2)
library(ggplot2)
library(ggpubr)
```

#####################
#
## Read the results
#
#####################
```{r}
gpredsA<-readRDS(here::here("output","genomicPredictions_additive.rds"))
gpredsAD<-readRDS(here::here("output","genomicPredictions_additive_plus_dominance.rds"))
gpredsDirDom<-readRDS(here::here("output","genomicPredictions_directional_dominance.rds"))
```

######################################
#
## Pull out the additive model data 
#
######################################
```{r}
table_add<-gpredsA$gblups[[1]]
table_add$POP<-"Population"
table_add$Model<-"Additive"
head(table_add)
```


####################################################
#
## Pull out the additive plus dominance model data 
#
####################################################
```{r}
table_non_add<-gpredsAD$gblups[[1]]%>% 
# Filter by GETGV values
filter(predOf=="GETGV") 
table_non_add$POP<-"Population"
table_non_add$Model<-"Non Additive"
head(table_non_add)
```


#################################################
#
## Pull out the directional dominance model data 
#
#################################################
```{r}
table_dir<-gpredsDirDom$gblups[[1]]%>% 
# Filter by GETGV values
filter(predOf=="GETGV") 
table_dir$POP<-"Population"
table_dir$Model<-"Directional Dominance"
head(table_dir)
```


#############################################
#
## Choosing the best parents additive model
#
#############################################
```{r}
top1000_add<-gpredsA$gblups[[1]] %>% 
# Arrange in descending order based on the SELIND
arrange(desc(SELIND)) %>% 
# I'll pick the top 1000 parents
slice(1:1000)
top1000_add$POP<-"Selected"
top1000_add$Model<-"Additive"
head(top1000_add)
```


#################################################
#
## Choosing the best parents non additive model
#
#################################################
```{r}
top1000_non_add<-gpredsAD$gblups[[1]]%>% 
# Filter by GETGV values
filter(predOf=="GETGV")  %>% 
# Arrange in descending order based on the SELIND
 arrange(desc(SELIND)) %>% 
# I'll pick the top 1000 parents
slice(1:1000)
top1000_non_add$POP<-"Selected"
top1000_non_add$Model<-"Non Additive"
head(top1000_non_add)
```


#################################################
#
## Choosing the best parents non additive model
#
#################################################
```{r}
top1000_dir<-gpredsDirDom$gblups[[1]]%>% 
# Filter by GETGV values
filter(predOf=="GETGV")  %>% 
# Arrange in descending order based on the SELIND
 arrange(desc(SELIND)) %>% 
# I'll pick the top 1000 parents
slice(1:1000)
top1000_dir$POP<-"Selected"
top1000_dir$Model<-"Directional Dominance"
head(top1000_dir)
```


##########################
#
## Merging data frames
#
##########################
```{r}
table_final=rbind(table_add,table_non_add, table_dir,top1000_add, top1000_non_add,top1000_dir)


table_final=reshape2::melt(table_final, id.vars=c("GID", "predOf", "POP","Model"))
head(table_final)
```

####################
#
## Subset by trait
#
####################
```{r}
DMCg=subset(table_final, table_final$variable=="DMCg")
CWLSD=subset(table_final, table_final$variable=="CWLSD")
CBroLS=subset(table_final, table_final$variable=="CBroLS")
CBliLS=subset(table_final, table_final$variable=="CBliLS")
StC=subset(table_final, table_final$variable=="StC")
PA=subset(table_final, table_final$variable=="PA")
logFRY=subset(table_final, table_final$variable=="logFRY")
logFSY=subset(table_final, table_final$variable=="logFSY")
SELIND=subset(table_final, table_final$variable=="SELIND")
```


##########
#
## Plots
#
##########

#########
#
## DMCg
#
#########
```{r}
# ordering by model
DMCg$Model= factor(DMCg$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

a= ggplot(DMCg,aes(x=Model,y=value,fill=POP)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("DMCg")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 a
```


##########
#
## CWLSD
#
##########
```{r}
# ordering by model
CWLSD$Model= factor(CWLSD$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

b= ggplot(CWLSD,aes(x=Model,y=value,fill=POP)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("CWLSD")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 b
```


###########
#
## CBroLS
#
###########
```{r}
# ordering by model
CBroLS$Model= factor(CBroLS$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

c= ggplot(CBroLS,aes(x=Model,y=value,fill=POP)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("CBroLS")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 c
```


###########
#
## CBliLS
#
###########
```{r}
# ordering by model
CBliLS$Model= factor(CBliLS$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

d= ggplot(CBliLS,aes(x=Model,y=value,fill=POP)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("CBliLS")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 d
```

#########
#
## StC
#
#########
```{r}
# ordering by model
StC$Model= factor(StC$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

e= ggplot(StC,aes(x=Model,y=value,fill=POP)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("StC")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 e
```


#########
#
## PA
#
#########
```{r}
# ordering by model
PA$Model= factor(PA$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

f= ggplot(PA,aes(x=Model,y=value,fill=POP)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("PA")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 f
```


##########
#
## logFRY
#
##########
```{r}
# ordering by model
logFRY$Model= factor(logFRY$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

g= ggplot(logFRY,aes(x=Model,y=value,fill=POP)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("logFRY")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 g
```


###########
#
## logFSY
#
###########
```{r}
# ordering by model
logFSY$Model= factor(logFSY$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

h= ggplot(logFSY,aes(x=Model,y=value,fill=POP)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("logFSY")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 h
```


###########
#
## SELIND
#
###########
```{r}
# ordering by model
SELIND$Model= factor(SELIND$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

i= ggplot(SELIND,aes(x=Model,y=value,fill=POP)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("SELIND")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 i
```


###########################################
#
## Arranging the plots in the same window
#
###########################################
```{r}
#require(lemon)
#grid_arrange_shared_legend(a,b,c,d,e,f,g,h,i, ncol=3, nrow=3, position="bottom")


figure=ggarrange(a,b,c,d,e,f,g,h,i,
          labels = c("A", "B","C","D","E","F","G","H","I"),
          ncol=5, nrow=2, common.legend = TRUE, legend="bottom")
figure
```


#################
#
## Saving plot
#
#################
```{r}
ggexport(figure,width = 800,
  height = 600, filename = "boxplot_GEBV_all.png")
```



##################################################
#
## Subset by trait without original population
#
##################################################
```{r}
DMCg1=subset(table_final, table_final$variable=="DMCg")%>%filter(POP!="Population")
CWLSD1=subset(table_final, table_final$variable=="CWLSD")%>%filter(POP!="Population")
CBroLS1=subset(table_final, table_final$variable=="CBroLS")%>%filter(POP!="Population")
CBliLS1=subset(table_final, table_final$variable=="CBliLS")%>%filter(POP!="Population")
StC1=subset(table_final, table_final$variable=="StC")%>%filter(POP!="Population")
PA1=subset(table_final, table_final$variable=="PA")%>%filter(POP!="Population")
logFRY1=subset(table_final, table_final$variable=="logFRY")%>%filter(POP!="Population")
logFSY1=subset(table_final, table_final$variable=="logFSY")%>%filter(POP!="Population")
SELIND1=subset(table_final, table_final$variable=="SELIND")%>%filter(POP!="Population")
```


##########
#
## Plots
#
##########

#########
#
## DMCg
#
#########
```{r}
# ordering by model
DMCg1$Model= factor(DMCg1$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

a= ggplot(DMCg1,aes(x=Model,y=value,fill=Model)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("DMCg")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 a
```


##########
#
## CWLSD
#
##########
```{r}
# ordering by model
CWLSD1$Model= factor(CWLSD1$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

b= ggplot(CWLSD1,aes(x=Model,y=value,fill=Model)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("CWLSD")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 b
```


###########
#
## CBroLS
#
###########
```{r}
# ordering by model
CBroLS1$Model= factor(CBroLS1$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

c= ggplot(CBroLS1,aes(x=Model,y=value,fill=Model)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("CBroLS")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 c
```


###########
#
## CBliLS
#
###########
```{r}
# ordering by model
CBliLS1$Model= factor(CBliLS1$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

d= ggplot(CBliLS1,aes(x=Model,y=value,fill=Model)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("CBliLS")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 d
```

#########
#
## StC
#
#########
```{r}
# ordering by model
StC1$Model= factor(StC1$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

e= ggplot(StC1,aes(x=Model,y=value,fill=Model)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("StC")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 e
```


#########
#
## PA
#
#########
```{r}
# ordering by model
PA1$Model= factor(PA1$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

f= ggplot(PA1,aes(x=Model,y=value,fill=Model)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("PA")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 f
```


##########
#
## logFRY
#
##########
```{r}
# ordering by model
logFRY1$Model= factor(logFRY1$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

g= ggplot(logFRY1,aes(x=Model,y=value,fill=Model)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("logFRY")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 g
```


###########
#
## logFSY
#
###########
```{r}
# ordering by model
logFSY1$Model= factor(logFSY1$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

h= ggplot(logFSY1,aes(x=Model,y=value,fill=Model)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("logFSY")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 h
```


###########
#
## SELIND
#
###########
```{r}
# ordering by model
SELIND1$Model= factor(SELIND1$Model, levels = c("Additive", "Non Additive", "Directional Dominance"))

i= ggplot(SELIND1,aes(x=Model,y=value,fill=Model)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     xlab('Model')+
     ggtitle("SELIND")+
     scale_fill_manual(values=c( "chartreuse3", "firebrick","dodgerblue"))+
     theme_update(plot.title = element_text(hjust = 0.5))+
     scale_x_discrete(labels=c("Additive" = "A", "Non Additive" = "AD","Directional Dominance" = "DirDom"))+
  #   scale_y_continuous(limits=c(0.45,0.7),breaks = c(0.2,0.25,0.3,0.35,0.4,0.45,0.5,0.55,0.6,0.65,0.7,0.75,0.8))+
     theme(strip.text = element_text(size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif"),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='bottom',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
 i
```


###########################################
#
## Arranging the plots in the same window
#
###########################################
```{r}
#require(lemon)
#grid_arrange_shared_legend(a,b,c,d,e,f,g,h,i, ncol=3, nrow=3, position="bottom")


figure1=ggarrange(a,b,c,d,e,f,g,h,i,
          labels = c("A", "B","C","D","E","F","G","H","I"),
          ncol=5, nrow=2, common.legend = TRUE, legend="bottom")
figure1
```


#################
#
## Saving plot
#
#################
```{r}
ggexport(figure1,width = 800,
  height = 600, filename = "boxplot_GEBV_selected_parents.png")
```


