---
title: "1_Prepare_phenotype_data"
author: "Paulo-HR"
date: "2023-10-21"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

#################
#
## Introduction
#
#################
```{r}
library(gt)
library(genomicMateSelectR)
library(plyr)
library(ggplot2)
```

##############################
#
## Importing phenotype data
#
###############################
```{r}
dbdata<-readDBdata(phenotypeFile = here::here("data","phenotype.csv"),
                   metadataFile = here::here("data","metadata.csv"))
```

##################################
#
## Checking experimental designs
#
##################################
```{r}
dbdata %>% dplyr::count(observationLevel)
dbdata %>% 
     dplyr::count(studyYear,studyName,trialType, studyDesign, numberBlocks,numberReps,entryType) %>% 
     spread(entryType,n) %>% 
     gt()  %>% 
     tab_options(table.font.size = pct(75))
```

##########################################################################################################
#
## check if the replicate and blockNumber columns reliably distinguish complete and incomplete blocks in     the data
#
##########################################################################################################
```{r}
dbdata %>% 
     group_by(studyYear,studyName) %>% 
     dplyr::summarize(N_replicate=length(unique(replicate)),
               N_blockNumber=length(unique(blockNumber))) %>% 
     gt() %>% tab_options(table.font.size = pct(75))
```

####################################################################
#
## Checking with there are complete replications of the experiment
#
####################################################################

```{r}
dbdata %>% 
     group_by(studyYear,studyName) %>% 
     dplyr::summarize(N_replicate=length(unique(replicate)),
               N_blockNumber=length(unique(blockNumber)),
               doRepsEqualBlocks=all(replicate==blockNumber)) %>% 
     gt() %>% tab_options(table.font.size = pct(75))
```

#########################################################################################################
#
## Checking that the replicate column definitely means complete blocks. If the numbers are very similar      for all trials, indicating complete blocks
#
#########################################################################################################
```{r}
dbdata %>% 
     group_by(studyName) %>% 
     dplyr::summarize(N_accession=length(unique(germplasmName))) %>% 
     # the average number of accessions per replicate per trial
     left_join(dbdata %>% 
                    group_by(studyName,replicate) %>% 
                    dplyr::summarize(N_accession=length(unique(germplasmName))) %>% 
                    group_by(studyName) %>% 
                    dplyr::summarize(avgAccessionsPerReplicate=ceiling(mean(N_accession)))) %>% 
     gt() %>% tab_options(table.font.size = pct(75))
```

##########################################################################
#
## Looking at the min, mean and max number of accessions per blockNumber
#
##########################################################################
```{r}
dbdata %>% 
     group_by(studyYear,studyName) %>% 
     dplyr::summarize(N_accession=length(unique(germplasmName))) %>% 
     left_join(dbdata %>% 
     group_by(studyName,replicate,blockNumber) %>% 
     dplyr::summarize(N_accession=length(unique(germplasmName))) %>% ungroup() %>% 
     group_by(studyName) %>% 
     dplyr::summarize(minAccessionsPerBlock=ceiling(min(N_accession)),
               avgAccessionsPerBlock=ceiling(mean(N_accession)),
               maxAccessionsPerBlock=ceiling(max(N_accession)))) %>% 
     gt() %>% tab_options(table.font.size = pct(60))
```


##################################################################################################
#
## Creating explicitly nested design variables (yearInLoc, trialInLocYr, repInTrial, blockInRep)
#
##################################################################################################
```{r}
dbdata %<>% 
     group_by(studyName) %>% 
     dplyr::summarize(N_replicate=length(unique(replicate)),
               N_blockNumber=length(unique(blockNumber)),
               doRepsEqualBlocks=all(replicate==blockNumber)) %>% 
     ungroup() %>% 
     mutate(CompleteBlocks=ifelse(N_replicate>1,TRUE,FALSE),
            IncompleteBlocks=ifelse(N_blockNumber>1 & !doRepsEqualBlocks,TRUE,FALSE)) %>% 
     left_join(dbdata) %>% 
     mutate(yearInLoc=paste0(programName,"_",locationName,"_",studyYear),
            trialInLocYr=paste0(yearInLoc,"_",studyName),
            repInTrial=paste0(trialInLocYr,"_",replicate),
            blockInRep=paste0(repInTrial,"_",blockNumber))
```


#############################################
#
## Checking complete and incomplete blocks
#
#############################################
```{r}
dbdata %>% 
     dplyr::count(studyYear,studyName,CompleteBlocks,IncompleteBlocks) %>% 
     left_join(dbdata %>% 
                    group_by(studyName) %>% 
                    dplyr::summarize(nRepInTrial=length(unique(repInTrial)),
                              nBlockInRep=length(unique(blockInRep)))) %>% 
     gt() %>% tab_options(table.font.size = pct(67))
```

#########################
#
## Renaming the traits
#
#########################
```{r}
traitabbrevs<-tribble(~TraitAbbrev,~TraitName,
        "FSW","fresh.shoot.weight.measurement.in.kg.per.plot.CO_334.0000016",
        "FRW","fresh.storage.root.weight.per.plot.CO_334.0000012",        
        "DMCg","dry.matter.content.by.specific.gravity.method.CO_334.0000160",
        "DMCo","dry.matter.content.percentage.CO_334.0000092",
        "NOHAV","plant.stands.harvested.counting.CO_334.0000010",
        "CWLSD","cassava.white.leaf.spot.disease.severity.by.visual.rating.1.5.CO_334.0002116",
        "CBroLS","cassava.brown.leaf.spot.disease.severity.by.visual.rating.1.5.CO_334.0002118",
        "CBliLS","cassava.blight.leaf.spot.disease.severity.by.visual.rating.1.5.CO_334.0002120",
        "StC","starch.content.percentage.CO_334.0000071",
        "PA","plant.architecture.visual.rating.1.5.CO_334.0000099")

traitabbrevs %>% gt()#rmarkdown::paged_table()
```


###################################
#
## Selecting columns from dbdata
#
###################################
```{r}
dbdata<-renameAndSelectCols(traitabbrevs,
                            indata=dbdata,
                            customColsToKeep = c("observationUnitName",
                                                 "CompleteBlocks",
                                                 "IncompleteBlocks",
                                                 "yearInLoc",
                                                 "trialInLocYr",
                                                 "repInTrial","blockInRep"))
```

#############################
#
## Fixing synonym naming 
#
############################
```{r}
#dbdata$germplasmName <- as.factor(dbdata$germplasmName)
#dbdata$germplasmName <-  revalue(dbdata$germplasmName,                                                       # #                               c("Conquista-2"="11-Conquista-2",
#                                     "BGM-0249(A.Marag)"="BGM-0249",
#                                     "Dimmy-22"="BGM-2179",
#                                     "IAC-12"= "BGM-2192",
#                                     "Lagoao"="BGM-2204",
#                                     "Ouro Pao"="BGM-2233",
#                                     "Sacai"= "BGM-2263",
#                                     "Guela-de-Jacu"="BGM-2304",
#                                     "032-09"="BGM-2325",
#                                     "Peru Preto"="BGM-2351"))
```

#########################################################
#
## Checking if all trait values are in allowable ranges 
#
#########################################################
```{r}
#dbdata<-dbdata %>% 
#     dplyr::mutate(DMCg=ifelse(DMCg<5 | DMCg>65,NA,DMCg),
#                   NOHAV=ifelse(NOHAV==0,NA,NOHAV),
#                   NOHAV=ifelse(NOHAV>42,NA,NOHAV),
#                   PA=ifelse(PA<0 | PA>5,NA,PA))
```

##########################################
#
## Computing plot area (meters squared)
#
##########################################
```{r}
dbdata %>% 
   dplyr::select(studyYear,studyName,studyDesign,plotWidth,plotLength,plantsPerPlot) %>% 
     dplyr::group_by(studyYear,studyName,studyDesign,plotWidth,plotLength,plantsPerPlot) %>% 
  count() %>%
     mutate(plotArea=plotWidth*plotLength) %>% 
     gt() %>% tab_options(table.font.size = pct(67))
```

########################################
#
## Ploting the area in meters squared 
#
########################################
```{r}
dbdata %>% 
     mutate(plotArea=plotWidth*plotLength) %>% 
     ggplot(.,aes(x=plotArea,y=NOHAV, fill=studyName)) + 
     geom_boxplot() + theme(axis.text.x = element_blank())
```

###########################################################################################
#
## Computing composite traits fresh root yield (FRY) and fresh shoot yield (FSY) - kg/m2
#
###########################################################################################

## Computing the mean average for FRY and FSY
```{r}
plantsPerPlot_choices<-dbdata %>% 
    dplyr::distinct(studyYear,studyName,plotWidth,plotLength,plantsPerPlot) %>% 
     dplyr::left_join(dbdata %>% 
                    dplyr::group_by(studyName) %>% 
                    dplyr::summarize(MaxNOHAV=max(NOHAV, na.rm=T),
                                     MeaFRW=mean(FRW,na.rm=T),
                                     MeaFSW=mean(FSW,na.rm=T),
                                     MeaDMCg=mean(DMCg,na.rm=T))) %>% 
          # plot area in meters squared
     dplyr::mutate(plotArea=plotWidth*plotLength,
            # Number of plants per plot
            plantsPerPlot=MaxNOHAV) %>% 
            #plantsPerPlot=ifelse(studyName=="19.GS.C2.UYT.36.setA.UB",20,plantsPerPlot)) 
  # exclude the empty genetic gain trial
     # filter(studyName!="BR.AYTGS.20.Ala") %>% 
     dplyr::select(studyName,plotArea,plantsPerPlot,MeaFRW,MeaFSW,MeaDMCg)

plantsPerPlot_choices %>% gt() #%>% tab_options(table.font.size = pct(67))%>%

```


```{r}
dbdata %<>%
     # remove the empty genetic gain trial
     filter(studyName!=c("BR.BAG5.PT.15.Citrus")) %>% 
     dplyr::select(-plantsPerPlot) %>% 
     # join plantsPerPlot_choices to the trial data
     left_join(plantsPerPlot_choices) 

dbdata %<>%
     # remove the empty genetic gain trial
     filter(studyName!=c( "BR.BAG.TP.19.CNPMF")) %>% 
     dplyr::select(-plantsPerPlot) %>% 
     # join plantsPerPlot_choices to the trial data
     left_join(plantsPerPlot_choices) 

dbdata %<>%
     # remove the empty genetic gain trial
     filter(studyName!=c( "BR.BAG1.Rec1.PT.18.Candeal")) %>% 
     dplyr::select(-plantsPerPlot) %>% 
     # join plantsPerPlot_choices to the trial data
     left_join(plantsPerPlot_choices) %>% 
    
  # compute fresh root yield (FRY) and fresh shoot yield (FSY) in tons per hectare
     mutate(FRY=(FRW*10)/plotArea,
            FSY=(FSW*10)/plotArea)

# Joining, by = "studyName"
dbdata %>% ggplot(.,aes(x=FRY,fill=studyName)) + geom_density(alpha=0.75)
dbdata %>% ggplot(.,aes(x=FSY,fill=studyName)) + geom_density(alpha=0.75)
```


################################
#
## log-transform yield traits 
#
################################
NOTE: this is a habit based on experience. Linear mixed-models should have normally distributed homoskedastic residuals, if they don’t log-transform the response variable often helps. For FYLD and related traits, I always log-transform.
```{r}
# I log transform yield traits 
# to satisfy homoskedastic residuals assumption 
# of linear mixed models
dbdata %<>% 
     mutate(logFRY=log(FRY),
            logFSY=log(FSY),
            PropNOHAV=NOHAV/plantsPerPlot) 
# remove non transformed / per-plot (instead of per area) traits
dbdata %<>% dplyr::select(-FRW,-FSW,-DMCo)
dbdata %>% ggplot(.,aes(x=logFRY,fill=studyName)) + geom_density(alpha=0.75)
dbdata %>% ggplot(.,aes(x=logFSY,fill=studyName)) + geom_density(alpha=0.75)
dbdata %>% ggplot(.,aes(x=DMCg,fill=studyName)) + geom_density(alpha=0.75)
dbdata %>% ggplot(.,aes(x=StC,fill=studyName)) + geom_density(alpha=0.75)
dbdata %>% ggplot(.,aes(x=PA,fill=studyName)) + geom_density(alpha=0.75)
dbdata %>% ggplot(.,aes(x=CWLSD,fill=studyName)) + geom_density(alpha=0.75)
dbdata %>% ggplot(.,aes(x=CBroLS,fill=studyName)) + geom_density(alpha=0.75)
dbdata %>% ggplot(.,aes(x=CBliLS,fill=studyName)) + geom_density(alpha=0.75)
```


#####################################
#
## Saving the "cleaned" phenotypes
#
#####################################
```{r}
saveRDS(dbdata,file=here::here("output","phenotypes_cleaned.rds"))
```
