---
title: "6_Standard_K-fold_Cross_validation_directional_dominance_effect"
author: "Paulo-HR"
date: "2023-10-21"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

##################
#
## Introduction
#
##################


#######################
#
## Calling packages
#
#######################
```{r}
library(genomicMateSelectR)
library(ggplot2)
library(plyr)
```


##############################
#
## Importing phenotype data
#
###############################
```{r}
blups<-readRDS(here::here("output","blups_fixed_labels.rds"))
```


###############################
#
## Genomic relationship matrix
#
###############################
```{r}
## Dominance relationship matrix
D<-readRDS(file=here::here("output","kinship_dom.rds"))
dim(D)

## Additive relationship matrix
A<-readRDS(file=here::here("output","kinship_add.rds"))
dim(A)
```

###################
#
## Dosage matrix
#
###################
```{r}
dosages<-readRDS(here::here("data","dosages.rds"))
dosages=dosages[order(rownames(dosages)), ]
dim(dosages)
```


########################################################
#
## Plotting off-diagonal values of the kinship matrix
#
########################################################
```{r}
hist(A[lower.tri(A)], main='Off-diagonal values (lower-triangle) of the kinship matrix')
```


#####################################################
#
## Plotting diagonal values of the kinship matrix
#
#####################################################
```{r}
hist(diag(A), main='Diagonals of the kinship', breaks=20)
```


############################
#
## Filtering by population
#
############################
```{r}
#    blups$blups[[1]]<-blups$blups[[1]] %>%  filter(POP=='C0')
#    blups$blups[[2]]<-blups$blups[[2]] %>%  filter(POP=='C0')
#    blups$blups[[3]]<-blups$blups[[3]] %>%  filter(POP=='C0')
#    blups$blups[[4]]<-blups$blups[[4]] %>%  filter(POP=='C0')
#    blups$blups[[5]]<-blups$blups[[5]] %>%  filter(POP=='C0')
```


#####################################
#
## Set-up for the cross-validation
#
#####################################
```{r}
blups %<>% 
     # need to rename the "blups" list to comply with the runCrossVal function
     dplyr::rename(TrainingData=blups) %>% 
     dplyr::select(Trait,TrainingData) %>% 
     # need also to remove phenotyped-but-not-genotyped lines
     # couldn't hurt to also subset the kinship to only phenotyped lines... would save RAM
     mutate(TrainingData=map(TrainingData,
                             ~filter(.,germplasmName %in% rownames(A)) %>% 
                                  # rename the germplasmName column to GID
                                 dplyr::rename(GID=germplasmName)))
 
```


############################################
#
## Sorting the data frame by germplasmName
#
############################################
```{r}
for(i in 1:nrow(blups)){
blups$TrainingData[[i]] <- blups$TrainingData[[i]][order(blups$TrainingData[[i]]$GID),]
}
blups
```

#####################################################################
#
## Deleting phenotyped-but-not-genotyped lines from kinship matrix
#
#####################################################################
```{r}
# For fastest, lightest compute of accuracy, remove non-phenotyped from kinship

gids<-blups %>%
  unnest(TrainingData) %$% unique(GID)

## Additive
A<-A[gids,gids]
A<-A[order(rownames(A)),order(colnames(A))]
dim(A)

## Dominance
D<-D[gids,gids]
D<-D[order(rownames(D)),order(colnames(D))]
dim(D)
```


#####################################################################
#
## Deleting phenotyped-but-not-genotyped lines from kinship matrix
#
#####################################################################
```{r}
## Additive
#A=subset(A,colnames(A)%in% gids)
#A=A[order(rownames(A)), ]
#A1=t(A)
#A2=subset(A1,rownames(A1)%in% gids)
#A2=A2[order(rownames(A2)),]
#dim(A2)

## Dominance
#D=subset(D,colnames(D)%in% gids)
#D=D[order(rownames(D)), ]
#D1=t(D)
#D2=subset(D1,rownames(D1)%in% gids)
#D2=D2[order(rownames(D2)), ]
#dim(D2)
```

########################################################
#
## Constructing a genomic relationship matrix vector
#
########################################################
```{r}
grms<-list(A=A,D=D)
```


#####################################################################
#
## Deleting phenotyped-but-not-genotyped lines dosages matrix
#
#####################################################################
```{r}
dosages1=subset(dosages,rownames(dosages) %in% gids)
dosages1 <- dosages1[order(rownames(dosages1)), ]
dim(dosages1)
```

#######################
#
## Selection indices
#
#######################
```{r}
SIwts<-c(DMCg=5,
         CWLSD=0,
         CBroLS=0,
         CBliLS=0,
         StC=10,
         PA=-8,
         logFRY=10,
         logFSY=8)
SIwts
```


########################
#
## Cross-validation
#
########################
```{r}
starttime<-proc.time()[3]
standardCV2<-runCrossVal(blups=blups,
                        modelType="DirDom",
                        selInd=TRUE,SIwts=SIwts,
                        grms=list(A=grms[["A"]],
                                  D=grms[["D"]]),
                        dosages= dosages1,
                        nrepeats=50,nfolds=5,
                        gid="GID",seed=424242,
                        ncores=32)
```


#######################
#
## Saving the results
#
#######################
```{r}
saveRDS(standardCV2,file = here::here("output","standardCV_directional_dominance.rds"))
```

############################
#
## Reading the results
#
############################
```{r}
predAS_DirDom<-readRDS(here::here("output","standardCV_directional_dominance.rds"))
```

######################
#
## Plotting results
#
######################
```{r}
predAS_DirDom %>% 
     unnest(accuracyEstOut) %>% 
     dplyr::select(repeats,id,predOf,Trait,Accuracy) %>% 
     filter(predOf=="GETGV") %>%  
      mutate(Trait = factor(Trait, levels = c('DMCg','CWLSD','CBroLS','CBliLS','StC', 'PA', 'logFRY','logFSY','SELIND'))) %>% 
     ggplot(.,aes(x=Trait,y=Accuracy,fill=Trait)) + 
     stat_boxplot(geom = "errorbar") +
     geom_boxplot()+ 
     stat_summary(fun="mean", geom="point", size=2,shape=8,
               position=position_dodge(width=0.75), color="black")+ 
     scale_fill_manual(values=c("darkblue","firebrick","chartreuse4","darkturquoise","#E69F00","#FC4E07","mediumvioletred","#66CC99","#999999"))+
     xlab('Group')+
     scale_x_discrete(labels=c("DMCg" = "DMCg", "StC" = "StC", "PA"="PA", "logFRY"="FRY","logFSY"="FSY","SELIND"="SELIND"))+
     scale_y_continuous(limits=c(-0.1,0.9),breaks = c(-0.2,-0.1,0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9))+
     theme(strip.text = element_text(hjust = -0, size=12,family="serif",face="bold"))+
     theme(axis.text.x = element_text(size=12,family="serif"))+
     theme(axis.text.y = element_text(size=12,family="serif"))+
     theme(axis.title.x = element_text(color="black", size=12,family="serif",),
          axis.title.y = element_text(color="black", size=12,family="serif"),
          legend.key.size = unit(0.5, "cm"),
          legend.position='none',
          legend.title = element_blank(),
          legend.text = element_text(colour = "black", size = 8,family="serif", face="bold"),
          legend.key = element_rect(colour = "transparent", fill = "white"),
          #panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.grid.major =element_line(color= "grey80", linetype = "solid", linewidth = 0.4),
          panel.background = element_rect(fill = "white",
                                        colour = "grey80"))
```

##############################################
#
## Data frame to estimate Accuracy average
#
##############################################
```{r}
AS_data=predAS_DirDom %>%
        group_by(accuracyEstOut) %>%
        unnest(accuracyEstOut)%>%
        filter(predOf=="GEBV")
```

######################
#
## Accuracy average
#
######################
```{r}
AS=as.data.frame(ddply(AS_data, "Trait", summarise, rating.mean=mean(Accuracy)))
colnames(AS)=c("Trait"," AS")
AS
```



